Operational Feature Selection with Gaussian Mixture Models for remote sensing images

### 2016-10-11 paper.tex
fix appendix

The python and C++ code are available freely for download: \url{https://github.com/Laadr/FFFS}, \url{https://github.com/Laadr/otbExternalFastFeaturesSelection}.

@@

\begin{proof}[Proof of proposition~(\ref{eq:update-quad})]
    \begin{alignat*}{3}
    (&\mathbf{x}^{(k)})^t && (\boldsymbol{\Sigma}^{(k)})^{-1} \mathbf{x}^{(k)}
       = \left[\begin{array}{cc} (\mathbf{x}^{(k-1)})^t   & x_k \end{array}\right]
                                                            \left[\begin{array}{cc}
                                                                    \mathbf{A}   & \mathbf{v} \\
                                                                    \mathbf{v}^t & \frac{1}{\alpha}
                                                                  \end{array}\right]
                                                                                   \left[\begin{array}{c} \mathbf{v} \\ x_k \end{array}\right] \\
     &= &&\left[\begin{array}{cc} (\mathbf{x}^{(k-1)})^t \mathbf{A} + x_k \mathbf{v}^t & (\mathbf{x}^{(k-1)})^t \mathbf{v} + \frac{x_k}{\alpha} \end{array}\right]
                                                                                       \left[\begin{array}{c} \mathbf{v} \\ x_k \end{array}\right] \\
     &= &&(\mathbf{x}^{(k-1)})^t \mathbf{A} \mathbf{x}^{(k-1)} + x_k \mathbf{v}^t \mathbf{x}^{(k-1)} + (\mathbf{x}^{(k-1)})^t \mathbf{v} x_k + \frac{(x_k)^2}{\alpha} \\
     &= &&(\mathbf{x}^{(k-1)})^t ((\boldsymbol{\Sigma}^{(k-1)})^{-1} + \frac{1}{\alpha} (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u} \mathbf{u}^t (\boldsymbol{\Sigma}^{(k-1)})^{-1}) \mathbf{x}^{(k-1)}\\
     & &&+ 2 x_k \mathbf{v}^t \mathbf{x}^{(k-1)} + \frac{(x_k)^2}{\alpha} \\
     &= &&(\mathbf{x}^{(k-1)})^t ((\boldsymbol{\Sigma}^{(k-1)})^{-1} + \alpha \mathbf{v} \mathbf{v}^t) \mathbf{x}^{(k-1)}\\
     & &&+ 2 x_k \mathbf{v}^t \mathbf{x}^{(k-1)} + \frac{(x_k)^2}{\alpha} \\
     &= &&(\mathbf{x}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{x}^{(k-1)} + \alpha ( (\mathbf{x}^{(k-1)})^t \mathbf{v} \mathbf{v}^t \mathbf{x}^{(k-1)} \\
     & &&+ 2 \frac{x_k}{\alpha} \mathbf{v}^t \mathbf{x}^{(k-1)} + \frac{(x_k)^2}{\alpha^2}) \\
     &= &&(\mathbf{x}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{x}^{(k-1)} + \alpha ( (\mathbf{x}^{(k-1)})^t \mathbf{v} + \frac{x_k}{\alpha} )^2 \\
     &= &&(\mathbf{x}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{x}^{(k-1)} + \alpha ( \left[\begin{array}{cc} \mathbf{v}^t & \frac{1}{\alpha} \end{array}\right] \mathbf{x}^{(k)} )^2
    \end{alignat*}
\end{proof}

\begin{proof}[Proof of proposition~(\ref{eq:update-log})]
    \begin{align*}
        \log \left(|\boldsymbol{\Sigma}^{(k)}|\right) =
        &\log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}^{(k-1)} & \mathbf{u}      \\
                \mathbf{u}^t          & \sigma_{kk} \\
            \end{array}\bigg]
        \right|\right) \\
        &\log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}^{(k-1)} & \mathbf{0}_{k-1,1}     \\
                \mathbf{u}^t          & 1 \\
            \end{array}\bigg]
            \bigg[\begin{array}{cc}
                \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u}      \\
                \mathbf{0}_{k-1,1}^t          & \sigma_{kk} - \mathbf{u}^t(\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u}\\
            \end{array}\bigg]
        \right|\right) \\
        &\log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}^{(k-1)} & \mathbf{0}_{k-1,1}     \\
                \mathbf{u}^t          & 1 \\
            \end{array}\bigg]
        \right|\right)
        +\log \left(\left|
            \bigg[\begin{array}{cc}
                \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u}      \\
                \mathbf{0}_{k-1,1}^t          & \alpha \\
            \end{array}\bigg]
        \right|\right) \\
        &\log \left( |\boldsymbol{\Sigma}^{(k-1)}| |1| \right) + \log \left( |\mathbf{I}_{k-1}| |\alpha| \right)\\
        &\log \left( |\boldsymbol{\Sigma}^{(k-1)}| \right) + \log ( \alpha )
    \end{align*}
\end{proof}

>>>>

The python and C++ code are available freely for download: \url{https://github.com/Laadr/FFFS}, \url{https://github.com/Laadr/otbFFSforGMM}.

@@

\begin{proof}[Proof of proposition~(\ref{eq:update-quad})]
    {\footnotesize
    \begin{alignat*}{3}
    (&\mathbf{x}^{(k)})^t && (\boldsymbol{\Sigma}^{(k)})^{-1} \mathbf{x}^{(k)}
       = \left[\begin{array}{cc} (\mathbf{x}^{(k-1)})^t   & x_k \end{array}\right]
        \left[\begin{array}{cc}
            \mathbf{A}   & \mathbf{v} \\
            \mathbf{v}^t & \frac{1}{\alpha}
        \end{array}\right]
        \left[\begin{array}{c} \mathbf{x}^{(k-1)} \\ x_k \end{array}\right] \\
     &= &&\left[\begin{array}{cc} (\mathbf{x}^{(k-1)})^t \mathbf{A} + x_k \mathbf{v}^t & (\mathbf{x}^{(k-1)})^t \mathbf{v} + \frac{x_k}{\alpha} \end{array}\right]
            \left[\begin{array}{c} \mathbf{x}^{(k-1)} \\ x_k \end{array}\right] \\
     &= &&(\mathbf{x}^{(k-1)})^t \mathbf{A} \mathbf{x}^{(k-1)} + x_k \mathbf{v}^t \mathbf{x}^{(k-1)} + (\mathbf{x}^{(k-1)})^t \mathbf{v} x_k + \frac{(x_k)^2}{\alpha} \\
     &= &&(\mathbf{x}^{(k-1)})^t ((\boldsymbol{\Sigma}^{(k-1)})^{-1} + \frac{1}{\alpha} (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u} \mathbf{u}^t (\boldsymbol{\Sigma}^{(k-1)})^{-1}) \mathbf{x}^{(k-1)}\\
     & &&+ 2 x_k \mathbf{v}^t \mathbf{x}^{(k-1)} + \frac{(x_k)^2}{\alpha} \\
     &= &&(\mathbf{x}^{(k-1)})^t ((\boldsymbol{\Sigma}^{(k-1)})^{-1} + \alpha \mathbf{v} \mathbf{v}^t) \mathbf{x}^{(k-1)}\\
     & &&+ 2 x_k \mathbf{v}^t \mathbf{x}^{(k-1)} + \frac{(x_k)^2}{\alpha} \\
     &= &&(\mathbf{x}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{x}^{(k-1)} + \alpha ( (\mathbf{x}^{(k-1)})^t \mathbf{v} \mathbf{v}^t \mathbf{x}^{(k-1)} \\
     & &&+ 2 \frac{x_k}{\alpha} \mathbf{v}^t \mathbf{x}^{(k-1)} + \frac{(x_k)^2}{\alpha^2}) \\
     &= &&(\mathbf{x}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{x}^{(k-1)} + \alpha ( (\mathbf{x}^{(k-1)})^t \mathbf{v} + \frac{x_k}{\alpha} )^2 \\
     &= &&(\mathbf{x}^{(k-1)})^t (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{x}^{(k-1)} + \alpha ( \left[\begin{array}{cc} \mathbf{v}^t & \frac{1}{\alpha} \end{array}\right] \mathbf{x}^{(k)} )^2
    \end{alignat*}
    }
\end{proof}

\begin{proof}[Proof of proposition~(\ref{eq:update-log})]
    {\footnotesize
    \begin{align*}
        \log &\left(|\boldsymbol{\Sigma}^{(k)}|\right) =
        \log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}^{(k-1)} & \mathbf{u}      \\
                \mathbf{u}^t          & \sigma_{kk} \\
            \end{array}\bigg]
        \right|\right) \\
        =&\log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}^{(k-1)} & \mathbf{0}_{k-1,1}     \\
                \mathbf{u}^t          & 1 \\
            \end{array}\bigg]
            \bigg[\begin{array}{cc}
                \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u}      \\
                \mathbf{0}_{k-1,1}^t          & \sigma_{kk} - \mathbf{u}^t(\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u}\\
            \end{array}\bigg]
        \right|\right) \\
        =&\log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}^{(k-1)} & \mathbf{0}_{k-1,1}     \\
                \mathbf{u}^t          & 1 \\
            \end{array}\bigg]
        \right|\right)
        +\log \left(\left|
            \bigg[\begin{array}{cc}
                \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}^{(k-1)})^{-1} \mathbf{u}      \\
                \mathbf{0}_{k-1,1}^t          & \alpha \\
            \end{array}\bigg]
        \right|\right) \\
        =&\log \left( |\boldsymbol{\Sigma}^{(k-1)}| |1| \right) + \log \left( |\mathbf{I}_{k-1}| |\alpha| \right)\\
        =&\log \left( |\boldsymbol{\Sigma}^{(k-1)}| \right) + \log ( \alpha )
    \end{align*}
    }
    \noindent where $\mathbf{I}_{k-1}$ is the $(k-1) \times (k-1)$ identity matrix and $\mathbf{0}_{k-1,1}$ is the $(k-1) \times 1$ null vector.

\end{proof}
